---
title: "Lab 01: Introduction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

This is our first "lab" of the semester. Each will be structured similarly,
with questions interwoven with code snippets. Note that they are numbered to
align with the class number. You should put the completed lab in your GitHub
repository ahead of the next class meeting.

## Testing

To start, let's just make sure R is running okay on your computer while
explaining the basic mechanism for using RMarkdown files. Below is a **code
chunk**. Click the green run button to execute the code. The result should
appear directly below.

```{r}
1 + 1
```

You can, and will, edit code chunks with your own R code. Use the chunk below
to calculate the sum of 1 and 2 and execute the code.

```{r}

```

In the RMarkdown labs you will also see within the text the words "Answer:".
This indicates that you need to type into the document your answer to a
question. Here is an example already filled in.

What does R think is the sum of 1 and 1?

**Answer**: 2

Now you try. What does R think is the sum of 1 and 2?

**Answer**:

## Further set-up

### Defaults

We need to set up a few more things before we are ready to go. First let's
reset some default in RStudio.

- In the RStudio menu click on `Tools > Global Options...`
- Look for the first drop-down: `Save the workspace to .RData on exit`
- Change this first drop-down to `Never`
- All of the check-boxes above this dropdown should be unchecked.

Do not skip these steps as you will run into trouble later in the course.

### Packages

The final step is to download all of the R packages that we will
need for the semester. It is generally easier to do these all at
once rather than as we go along.

To install the packages required for class, run the following lines
of code in the console. There may be a warning about one or two
packages not being available. Note that this may take 5-10 minutes
to finish; on slower connections or older computers, it may take even
longer. If you run into any problems, please let me know!

```{r, eval = FALSE}
pkgs <- c("dplyr", "ggplot2", "stringr", "ggmap", "ggrepel",
          "devtools", "viridis", "plotly", "jsonlite", "lazyeval",
          "knitr", "readr", "forcats", "Hmisc")

install.packages(pkgs,
                 repos = "https://cloud.r-project.org",
                 type = "binary",
                 dependencies = TRUE)
```

Now, you will also need install the `smodels` package. I have written
this package for this course, so you need to install it in a slightly
different way.

```{r, eval = FALSE}
devtools::install_github("statsmaths/smodels")
```

Once this is done you are all ready to hand in the first lab.

## Submission

You are now ready to submit the first lab. Save the file in RStudio through the
menu interface (standard keyboard shortcuts work as well). Now, log into your
GitHub account and drag the file into your repository. Make sure to then scroll
to the bottom of the package and "commit" the file. You will have to do this
for each assignment this semester.
